Data

### 2019-09-26 analysis/data.Rmd
correct data filename on google

```{bash ,eval=FALSE}
# enable relevant Python virtual environment (Python 2) if you have one, and you should.
$ pyenv activate anaconda2-4.2.0
$ cd data-raw
$ gsutil cp \
    gs://pru-trajectories/sources/merged/overnight_cpr_fr24/raw_cpr_fr24_positions_2017-08-08.csv.bz2 .
```

>>>>

```{bash ,eval=FALSE}
# enable relevant Python virtual environment (Python 2) if you have one, and you should.
$ pyenv activate anaconda2-4.2.0
$ cd data-raw
$ gsutil cp \
    gs://pru-trajectories/products/synth_positions/cpr_fr24/mas_05_cpr_fr24_synth_positions_2017-08-03.csv.bz2 .
```
